Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
better explanation.
Fix typo

\begin{itemize}
\item
    We originally implemented Doctest in Haskell and
    extended Haddock markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

The standard documentation mechanism for Haskell is
Haddock.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, the {\tt filepath} package and
the {\tt containers} package adopt this style.
Here is an example from the latter.

>>>>

\begin{itemize}
\item
    We originally implemented Doctest in Haskell and
    extended Haddock's markup to support examples, back in 2010
\item
    Add support for QuickCheck properties to Doctest and
    extend Haddock markup to support properties
    (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

For Doctest, we should use Haddock markup to express evidence.
Haddock has markup support for code blocks.  And it is widely used to
include properties and examples in documentation.
For instance, the {\tt filepath} package and
the {\tt containers} package adopt this style.
Here is an example from the latter.
